Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-06-04 sections0.03/results0.03.tex
PB finished editing section 4.1.1

            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups. 
            5 groups in the left side neurons were separated from 7 groups in the right side of the map with two dark-grey colours between them.
            This shows that even though the galaxies are clustered in twelve groups, there still remains only two main distinct groups.
            The closest occupied neurons in the starburst side of the SOM, belongs to the SB6 type. 
            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other starburst types.

            The fact that the galaxies needs to have at least 22 different neurons to be divided into 12 groups, shows that the differences between SB1 and SB2, and B and E galaxies are very small.
            Because of their similarities, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.

>>>>

            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups:
            5 groups in the left-side neurons are separated from 7 groups on the right side of the map with two dark-grey colours between them.
            This shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
            The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
            This template has the most extinction and its SED has more similarity to early type galaxies than other starburst types.

            The fact that the templates need to have at least 22 different neurons to be divided into 12 groups shows that the differences between SB1 and SB2, and B and E, templates are very small.
            Because of their similarities, they tend to stay in the same group until the network becomes big enough to make attention to the smallest particularity.
